
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
\secretcontent{}  % 将这里的括号内文字修改为空白即可保持下划线，同时没有任何文字显示。

\ctitle{在BESIII上研究正反重子对产生及其衰变}
% 根据自己的情况选，不用这样复杂
\makeatletter

\makeatother

\cdegree{理学博士}  %
\cdepartment[高能所]{中国科学院高能物理研究所}
\cmajor{粒子物理和原子核物理}  % 二级学科专业名称
\cauthor{马新鑫} 
%\cauthor{马\hspace{0.5em}新鑫} 
\csupervisor{李海波\hspace{1em}研究员}
\csupervisorplace{中国科学院高能物理研究所}
% 如果没有副指导老师或者联合指导老师，把下面两行相应的删除即可。


% 日期自动生成，如果你要自己写就改这个cdate
%\cdate{2018年6月} % 年月用阿拉伯数字填写，Times New Roman体四号加粗，夏季毕业填写6月，冬季填写12月

\etitle{Study the production and decay of baryon pair} 

\edegree{Doctor of Philosophy}

\eauthor{Xin-Xin Ma}
\edepartment{Institute of High Energy Physics\\Chinese Academy of Sciences}
\emajor{Particle Physics and Nuclear Physics}   %专业名称，具体填一级专业和二级专业，请咨询你们的老师
\esupervisor{Hai-Bo Li}

% 这个日期也会自动生成，你要改么？
% \edate{December 2016}

% 定义中英文摘要和关键字
\begin{cabstract}
    研究正反重子对的产生及其衰变的性质具有重要的物理意义。
    北京谱仪~III~是世界上唯一的在粲强子的产生阈值上获取数据的实验装置，
    收集了世界上最大的量子关联的粲介子数据样本，
    同时收集了世界上最大的来自正负电子对撞的$J/\psi$数据样本，
    提供了研究重子物理的理想平台。
    本文在奇异粲介子中寻找衰变$D_{s}^{+} \to p \bar{p} e^{+} \nu_{e}$，
    未看到显著的信号，并首次在$90\%$的置信度下设立了上限，
    $B(D_{s}^{+} \to p \bar{p} e^{+} \nu_{e}) < 2.0 \times 10^{-4} $。
    利用$J/\psi$数据样本，本文研究了$\Sigma^{0}\bar{\Sigma}^{0}$的产生
    的性质，测量了衰变参数$\alpha_{J/\psi}$和$\Delta \phi$，并发现了
    末态$\Sigma^{0}$部分极化的证据。我们另外讨论了$\Sigma^{0} \to \Lambda
    \gamma$过程的P宇称守恒及CP守恒，没有发现破坏的迹象。利用$\Sigma^{0}\bar{\Sigma}^{0}$
    样本，我们研究了$\Sigma^{0}$的达利兹衰变过程$\Sigma^{0} \to \Lambda e^{+} e^{-}$，用来寻找
    $X(17)$的存在迹象。受统计量的限制，$e^{+}e^{-}$的不变质量谱没有显示出明显的$X(17)$信号。

\end{cabstract}

\ckeywords{粲物理, 重子, 极化, CP-破坏, 形状因子}

\begin{eabstract} 
    Study the production and baryond pairs at the is of great important. BESIII is the unique experiment 
    which work at the threshold of charm meson, collecting the largest date set of charm meson, also 
   collecting the largest data set of $J/\psi$ meson. Those data sample provides an ideal place to study the baryond
   physics.  We try to search the $p\bar{p}$ pair producted by strange charm meson, the only one possible decay is 
   $D_{s}^{+} \to p \bar{p} e^{+} \nu_{e}$. So we perform a blind analysis, but no significance signal is observed since 
    we open the box. Then one upper limmit at $90\%$ confidence level is set, 
   $B(D_{s}^{+} \to p \bar{p} e^{+} \nu_{e}) < 2.0 \times 10^{-4} $.  Based on the largest $J/\psi$ sample, we study the 
   production of  $\Sigma^{0}\bar{\Sigma}^{0}$ pairs. The decay parameters $\alpha_{J/\psi}$ and $\Delta \phi$ are       measured, also an evidence of the polarization of  $\Sigma^{0}$ is found with $4.2 \sigma$. We also discuss the P-parity
   and CP-parity conservation in the decay of $\Sigma^{0} \to \Lambda \gamma$, no clue of P violation or CP violation found. Beside, using the $\Sigma^{0}$ sample, we study the dalitz decay $\Sigma^{0} \to \Lambda e^{+} e^{-}$, and 
  search for the $X(17)$, up to date, we have not found any evidence of $X(17)$. 

\end{eabstract}

\ekeywords{charm, baryon, polarization, CP-violation, form factor}
